\tool: A Multi-Mode BadUSB Device

### 2021-01-08 WOOT/Files/badusb.tex
complete impl part

As there were various Rubber Ducky implementation available, we only focus on its core functionality and our extension. Based on this pattern, we summaries our implementation of \tool into the following parts:

\begin{itemize}
	\item\textit{Hardware specification} the  hardware we uses to build \tool
	\item\textit{Scripting mode} functions like the original Rubber Ducky featuring the bypass of defense mechanism like USBCheckIn\cite{usbcheckin}
	\item \textit{Remote control mode} allows attacker to take complete control of victim's device manually to perform delicate operation.
	\item \textit{Privacy extraction mode} captures and identify private data from the victim and send to the attacker.
\end{itemize}
\subsubsection{Hardware Specification}
The hardware we use is as follows and the relation between them is illustrated at Fig.~\ref{fig:hardware_specification}
\begin{itemize}
	\item\textit{USB 3.x Hub} exports the USB 3.x connector into various ports, like DisplayPort, USB 2.0 port etc.
	\item\textit{Video Capture Card} convert DisplayPort signal into UVC-compatible\hongyi{citation needed} data, which is later processed by Raspberry Pi.
	\item\textit{Raspberry Pi} processes video stream from the victim where private data is extracted and transmitted through GSM/WiFi.
	\item\textit{Rubber Ducky} emulates HID device which can be controlled from either the embedded Raspberry Pi or the attacker.
\end{itemize}
\begin{figure}[hbtp]
	\includegraphics[width=\linewidth]{./Figs/hardware_specification.png}
	\caption{Hardware Specification}
	\label{fig:hardware_specification}
\end{figure}
\subsubsection{Scripting Mode}
\tool under this mode works almost the same like the original Rubber Ducky with various improvement.

@@

As the mouse relies on the visual feedback to work properly, its emulation were not supported by the original version of Rubber Ducky. Yet with the video output support from USB 3.x, our \tool implements full-functional mouse emulation. This function enables attacks toward pure GUI programs and showed great potential in mobile attack scenario. Details can be obtained in Section~\ref{sec:experiment}.
\subsubsection{Remote Control Mode}
\subsubsection{Privacy Extraction Mode}

>>>>

As there were various Rubber Ducky implementation available, we only focus on its core functionality and our extension. Based on this pattern, we summaries our implementation of \tool into the following parts and their comparison can be found in Table~\ref{table:mode_comparison}:
\begin{table*}
	\centering
	\begin{tabular}{|c|c|c|c|c|}
	\hline
	Mode & Detectibility & Automation & Power Consumption  \\
	\hline
	Scripting & Medium & Yes & Low\\
	\hline
	Remote Control & High & No & High \\
	\hline
	Privacy Extraction & Low & Yes & Medium\\
	\hline
	\end{tabular}
	\linebreak
	\caption{Comparison of Different Mode}
	\label{table:mode_comparison}
\end{table*}
\begin{itemize}
	\item\textit{Hardware specification} the  hardware we uses to build \tool
	\item\textit{Scripting mode} functions like the original Rubber Ducky featuring the bypass of defense mechanism like USBCheckIn\cite{usbcheckin}
	\item \textit{Remote control mode} allows attacker to take complete control of victim's device manually to perform delicate operation.
	\item \textit{Privacy extraction mode} captures and identify private data from the victim and send to the attacker.
\end{itemize}

\subsubsection{Hardware Specification}
The hardware we use is as follows and the relation between them is illustrated at Fig.~\ref{fig:hardware_specification}
\begin{itemize}
	\item\textit{USB 3.x Hub} exports the USB 3.x connector into various ports, like DisplayPort, USB 2.0 port etc.
	\item\textit{Video Capture Card} convert DisplayPort signal into UVC-compatible\hongyi{citation needed} data, which is later processed by Raspberry Pi.
	\item\textit{Raspberry Pi} processes video stream from the victim where private data is extracted and transmitted through GSM/WiFi.
	\item\textit{Rubber Ducky} emulates HID device which can be controlled from either the embedded Raspberry Pi or the attacker.
\end{itemize}
\begin{figure}[hbtp]
	\includegraphics[width=\linewidth]{./Figs/hardware_specification.png}
	\caption{Hardware Specification}
	\label{fig:hardware_specification}
\end{figure}
\subsubsection{Scripting Mode}
\tool under this mode works almost the same like the original Rubber Ducky with various improvement.

@@

As the mouse relies on the visual feedback to work properly, its emulation and automation were not supported by the original version of Rubber Ducky. Yet with the video output support from USB 3.x, our \tool implements full-functional mouse emulation. This function enables attacks toward pure GUI programs and showed great potential in mobile attack scenario. Details can be obtained in Section~\ref{sec:experiment}.
\subsubsection{Remote Control Mode}
In \tool, we implement all components required to operate a computer/mobile remotely, including a video stream, keyboard/mouse emulation.

\tool under this mode follows a simple logic. \tool will receive video stream from the victim's device and redirect it to the attacker via GSM/WiFi. In the meanwhile, \tool also receives commands from the attacker through GSM/WiFi and replay them to the victim by USB emulation.

This mode enable attacker to perform delicate operation that is beyond automation. Moreover, this mode provides a backdoor that does not require host network and thus is undetectable by firewall running on the host machine.
\hongyi{I think this is a quite good selling point?}
\subsubsection{Privacy Extraction Mode}
\tool under this mode does not emulate other USB device and solely rely on the video stream function of USB 3.x.

When running in this mode, \tool passively process the victim's video stream and detect for ``valuable'' private data.  Here, a data is ``valuable'' or not is decided by a customized detector, we implement a simple one of payment code for demonstration purpose. Though this detector is simple to implement, we successfully transfer money from the victim. More detail can be obtained in Section~\ref{sec:experiment}.

It is worth mentioning that \tool under this mode is completely passive, making it hard to be detected and defended. With different detector implemented, \tool under this mode is capable of serving more purpose.
